Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-22 PNAS/index.Rnw
Fixing intro

\firstpage[4]{7}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{koehlerFingerprintErrorRate2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.
%
\hh{In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.}
%
\hh{In order to avoid embarassing false accusation and a further erosion of the public's trust in science, we need to address the problem of multiple comparisons by controlling their effect on false discovery rates.}
%
\hh{Database searches are an example where the number of searches is explicitly available as the number of objects meeting the search criteria. }

@@

 \hh{Algorithms, in particular, make a large number of implicit comparisons out of a user's sight. The cross-correlation function, for example, has been suggested \citep{vorburgerApplicationsCrosscorrelationFunctions2011} as one of the first quantitative measures in response to the NAS report \citep{nas2009}, and is used in most pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity. }
\hh{Finding the best} \svp{alignment} \hh{requires implicitly} \svp{sliding} \hh{one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source and} \svp{keeping} \hh{track of the similarity measure.}
\svp{This mirrors the forensic examination process, as examiners visually}
rotate or align two pieces of evidence under comparison microscopes.

>>>>

\firstpage{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

This issue has been raised in the past with regard to DNA \citep{thompson2003} and fingerprints \citep{koehlerFingerprintErrorRate2021}: one of the issues \citep{fine2006} leading to the wrongful accusation of Brandon Mayfield in the 2004 Madrid bombing case was that the large size of the IAFIS database used to locate similar prints made it possible to locate `unusually' similar non-matches.
\svp{Very close non-matches are a direct consequence of a large number of comparisons; they will occur more frequently as databases increase in size and algorithms become more powerful.}
% In this paper, we discuss that very close non-matches are far from an unusual phenomenon  but a direct consequence of a large number of comparisons, and simply reflect the power of the search algorithms.
%
In order to avoid embarassing false accusations and a further erosion of the public's trust in science, we need to address the problem of multiple comparisons by controlling their effect on false discovery rates.
%
% \hh{Database searches are an example where the number of searches is explicitly available as the number of objects meeting the search criteria. } % This doesn't seem super-relevant and distracts from the continuity between the algorithm discussion above and the next paragraph

@@

Algorithms make a large number of comparisons \svp{that are not obvious to the user}
%out of a user's sight.
The cross-correlation function, for example, \svp{was} \citep{vorburgerApplicationsCrosscorrelationFunctions2011} one of the first quantitative measures \svp{proposed} in response to the NAS report \citep{nas2009}, and is used in \svp{many} pattern searching algorithms to find the best alignment between two sources and also evaluate the overall similarity.
Finding the best \svp{alignment} requires implicitly sliding one source across the whole length (for one-dimensional sources, such as striations) or area (for two dimensional sources, such as impression marks) of the other source \svp{ while keeping} track of \svp{the value of a} similarity measure.
\svp{This mirrors the forensic examination process, as examiners visually}
rotate or align two pieces of evidence under comparison microscopes.
